\textbf{Species and genus plant classification with NEON hyperspectral remote sensing data}

### 2020-11-04 R/clean_spectral_data.Rmd
added figure with spectra
made it taller vertically and make all the spectra one color for now

Visualize the spectra, facet by scientific name, color by taxon rank. 
```{r, warning=FALSE, fig.height=12, fig.width=16}
filtered_spectra %>%
  ggplot(aes(wavelength_nm, ifelse(mask, NA, reflectance), group = spectraID,
             # color each facet plot based on taxonRank
             color = taxonRank)) +
  geom_path(alpha = .2) +
  labs(x = '\n Wavelength (nm)',
       y = 'Reflectance \n',
       color = "Taxon Rank") + 
  facet_wrap(~genusSpecies
             # wrap long scientific names
             ,labeller = label_wrap_gen(20)
             ,ncol=10) + 
  scale_color_manual(values = c("#e6550d","#1c9099", "#a8ddb5")) + 
  theme_minimal() + 
  # Adjust the text size and rotation angle 
  theme(text = element_text(size=11),
        axis.text.x = element_text(angle=90, hjust=1),
        axis.title.y = element_text(size = 14),
        axis.title.x = element_text(size = 14),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 14))
```

>>>>

Visualize the spectra, facet by scientific name, color by taxon rank. 
```{r, eval = FALSE, include = "FALSE", warning=FALSE, fig.height=12, fig.width=16}
filtered_spectra %>%
  ggplot(aes(wavelength_nm, ifelse(mask, NA, reflectance), group = spectraID,
             # color each facet plot based on taxonRank
             color = taxonRank)) +
  geom_path(alpha = .2) +
  labs(x = '\n Wavelength (nm)',
       y = 'Reflectance \n',
       color = "Taxon Rank") + 
  facet_wrap(~genusSpecies
             # wrap long scientific names
             ,labeller = label_wrap_gen(20)
             ,ncol=10) + 
  scale_color_manual(values = c("#e6550d","#1c9099", "#a8ddb5")) + 
  theme_minimal() + 
  # Adjust the text size and rotation angle 
  theme(text = element_text(size=11),
        axis.text.x = element_text(angle=90, hjust=1),
        axis.title.y = element_text(size = 14),
        axis.title.x = element_text(size = 14),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 14))
```

Color all the spectra with a single color

```{r, eval = FALSE, include = "FALSE", warning=FALSE, fig.height=12, fig.width=16}
filtered_spectra %>%
  ggplot(aes(wavelength_nm, ifelse(mask, NA, reflectance), group = spectraID)) +
  geom_path(alpha = .2, color = "#1c9099") +
  labs(x = '\n Wavelength (nm)',
       y = 'Reflectance \n') + 
  facet_wrap(~genusSpecies
             # wrap long scientific names
             ,labeller = label_wrap_gen(20)
             ,ncol=5) +
  theme_minimal() + 
  # Adjust the text size and rotation angle 
  theme(text = element_text(size=11),
        axis.text.x = element_text(angle=90, hjust=1),
        axis.title.y = element_text(size = 14),
        axis.title.x = element_text(size = 14))

# save figure to file
ggsave(filename = here::here("analysis","figures", "spectra_per_species.pdf"), width = 10, height = 12)
```

Color the spectra by the year they were collected?

```{r, eval=FALSE, include=FALSE}
filtered_spectra %>%
  ggplot(aes(wavelength_nm, ifelse(mask, NA, reflectance), group = spectraID, color = as.factor(year))) +
  geom_path(alpha = .2) +
  labs(x = '\n Wavelength (nm)',
       y = 'Reflectance \n',
       color = "Year collected") + 
  facet_wrap(~genusSpecies
             # wrap long scientific names
             ,labeller = label_wrap_gen(20)
             ,ncol=10) + 
  scale_color_manual(values = c("#e6550d","#1c9099", "#a8ddb5")) + 
  theme_minimal() + 
  # Adjust the text size and rotation angle 
  theme(text = element_text(size=11),
        axis.text.x = element_text(angle=90, hjust=1),
        axis.title.y = element_text(size = 14),
        axis.title.x = element_text(size = 14),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 14))
```

### 2020-11-04 analysis/paper/paper.Rmd
added figure with spectra
made it taller vertically and make all the spectra one color for now

@@

```{r fig-studyArea, fig.cap ="Study Area", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
library(here)
knitr::include_graphics(here::here("analysis", "figures", "study_area.pdf"))
```

@@

```{r fig-histSpecies, fig.cap ="Histogram: spectra count per species", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
library(here)
knitr::include_graphics(here::here("analysis","figures", "hist_samples_per_species.pdf"))
```

@@

>>>>

Show the spectra for each scientific name class (Figure \@ref(fig:fig-plotSpectra)).

@@

```{r fig-studyArea, fig.cap ="Map", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
library(here)
knitr::include_graphics(here::here("analysis", "figures", "study_area.pdf"))
```

@@

```{r fig-histSpecies, fig.cap ="Histogram", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
library(here)
knitr::include_graphics(here::here("analysis","figures", "hist_samples_per_species.pdf"))
```

@@

```{r fig-plotSpectra, fig.cap ="Spectra", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
library(here)
knitr::include_graphics(here::here("analysis","figures", "spectra_per_species.pdf"))
```
